---
title: Inserting Coded Comments into Output Text Appendices
---

QualtricsTools not only makes it easy to create reports of text appendices, but 
also to create text appendices with frequency reports of categorized "coded comments."
Coded comments must follow one of two standardized formats correspond to 
how Tufts OIR exports coded commment data. The parameter `code_type` specifies whether
the coded comment data are exported from FileMaker Pro (or have been modified to appear as such)
or exported from NVivo using the crosstab export.

Use the function `make_coded_comments` to generate text appendices with coded comment tables.
the related function `make_split_coded_comments` will create split report coded comment appendices.

Both of the above functions accept an `n_threshold` parameter. This is the threshold for which coded comments frequency tables with a total number of responses less than `n_threshold` are not included. The parameter defaults to 15 if it is not specified.

Examples of coded comment data exports for each format are included in the QualtricsTools package.
In the prescribed workflow, each individual text entry component of a survey 
which needs to be categorized must have a corresponding coded comments xlsx file
in a directory. However, in this example we will only use coded comments 
for a single text entry component. 

### NVivo Crosstab Export

When coding comments with NVivo, use the matrix export for each note to produce a coded comment table
compatible with QualtricsTools. Coded comments using the `code_type` specification 
"nvivo" contain an unlabeled first column
of ResponseIDs. The second column is labeled with the variable name and includes 1's and 0's indicating
response presence for each respondent. The variable name in the second column header will be used to link
coded comment responses to the appropriate survey question as part of the QualtircsTools setup process. 
Unlike FileMaker exports, this NVivo matrix export cna include data for all respondents,
regardless of whether they responded to the question and have coded comment data. Columns to the right of this ResponseID column contain the coded comment categories as headers with 1's and 0's indicating whether 
the response was assigned to that category. Crosstab exports from NVivo
may also contain a "Total" column. This "Total" column is not necessary and will be ignored
when creating the coded comment table.

Sample data are shown below to illustrate the `code_type = "nvivo"` data export format.

```{r nvivo-data-export-sample, echo=FALSE, message = FALSE}
library(QualtricsTools)
nvivo_data_path <- here::here("data/Sample Surveys/Better Sample Survey/Comment Coding NVivo/Q5 Coded_NVivo.xlsx")
coded_comment_nvivo <- readxl::read_excel(nvivo_data_path,.name_repair = "minimal")
options(knitr.kable.NA = '')
knitr::kable(coded_comment_nvivo, format='markdown')

```

### FileMaker Pro Export
Coded comments using the code_type specification "fmp" contain "ResponseID" 
in the first column and a column titled "varname" with the variable name
values in each row. To the right of the "varname" column, is a column labeled with the question text,
containg full response text for each respondent. To the right of this question text, each column title 
represents a category which have "1" entries in cells to represent a respondent's
response being categorized into the given category. 

For a couple years after switching to comment coding in NVivo, OIR procedures involved exporting from NVivo 
and then coercing data to FMP format so that the coded comment export data would be compatible with QualtricsTools.
Updates in April have added compatability with NVivo matrix exports without requiring modification. However, 
old reports that have coded comments prepared according to former guidelines may require using the 
code_type "fmp" specification.

Sample data are shown below to illustrate the `code_type = "fmp"` data export format.

```{r fmp-data-export-sample, echo=FALSE, message = FALSE}
library(QualtricsTools)
fmp_data_path <- here::here("data/Sample Surveys/Comment Coding/Coded Comments/Q5 Coded.xlsx")
coded_comment_fmp <- readxl::read_excel(fmp_data_path)
options(knitr.kable.NA = '')
knitr::kable(coded_comment_fmp, format='markdown')

```

### Sample Output from make_coded_comments

Below is a sample of the coded comment appendix file created using make_coded comments.
In this example, I have specified `n_threshold = 5` since there are only six responses
to the text question q5_position.



```{r load_coded_comment_data, echo=FALSE}
library(shiny)
library(QualtricsTools)

# Grab the sample survey data from our repository.
qsf <- RCurl::getURL("https://raw.githubusercontent.com/emma-morgan/QualtricsTools/master/data/Sample%20Surveys/Better%20Sample%20Survey/Better_Sample_Survey.qsf")
csv <- RCurl::getURL("https://raw.githubusercontent.com/emma-morgan/QualtricsTools/master/data/Sample%20Surveys/Better%20Sample%20Survey/Better_Sample_Survey.csv")

# Write the sample survey data to file.
qsf_tempfile_path = tempfile()
csv_tempfile_path = tempfile()
write(x = qsf, file = qsf_tempfile_path)
write(x = csv, file = csv_tempfile_path)

# Download the sample coded comments
url <- "https://github.com/emma-morgan/QualtricsTools/blob/master/data/Sample%20Surveys/Comment%20Coding/Coded%20Comments/Q5%20Coded.xlsx?raw=true"
coded_comments_directory <- file.path(tempdir(), basename(tempfile(pattern="")))
dir.create(path = coded_comments_directory)
filename <- "Q5 Coded.xlsx"
coded_comments_filepath <- file.path(coded_comments_directory, filename)
download.file(url, coded_comments_filepath, mode="wb")
```

```{r echo=FALSE, message=FALSE}
output_filepath <- make_coded_comments(
  qsf_path = qsf_tempfile_path,
  csv_path = csv_tempfile_path,
  headerrows = 3, 
  sheets_dir = coded_comments_directory,
  n_threshold = 0,
  filename = "ExampleHTMLCodedComments.html",
  code_type = "fmp"
)
```

```{r}
# We use the includeHTML function from the shiny package to 
# render the HTML output.
includeHTML(output_filepath)
```


The `n_threshold` parameter which is passed above as 0 is the threshold for which coded comments frequency tables with a total number of responses less than `n_threshold` are not included. The parameter defaults to 15 if it is not specified. For example, when we render the report with the `n_threshold = 15` default parameter we see that the coded comments frequency table is not included in the report:

```{r}
output_filepath <- make_coded_comments(
  qsf_path = qsf_tempfile_path,
  csv_path = csv_tempfile_path,
  headerrows = 3, 
  sheets_dir = coded_comments_directory,
  filename = "ExampleHTMLCodedComments.html",
  code_type = "fmp"
)

shiny::includeHTML(output_filepath)
```

### Using Command Line Functions to Create Coded Comment Appendices

There are two functions to create coded comment appendices:

1. **make_coded_comments** creates coded comment appendix for an overall survey summary report
2. **make_split_coded_comments** creates coded comment appendices for split supgroup reports

Both of these functions require the following arguments (input):


* **qsf_path**: The path location of the .qsf file to be processed. This must be passed as text string (surrounded by "") 
and, on a Windows machine, all '\' must be replaced by '/'. If no qsf_path is provided, the user will be asked to choose 
a qsf.

* **csv_path**: The string path location of the .csv file to be processed. This requires path specifications as above. 
If no csv_path is provided, the user will be prompted to choose from the dialogue box.

* **headerrows**: Specifies the number of header rows in the CSV data. 
Use 3 for data exported under current OIR specifications (legacy exporter, unchecked legacy view results)

* **sheets_dir**: The string path location of the directory which contains Excel documents for each coded comment 
using one of the two formats specified. All coded comments must use the same data output format that follows the 
NVivo or FileMaker Pro export format.

* **output_dir**: The string path for the directory to which R should write the coded comment report. If not specified,
your coded comment appendix will be written to a temporaryy file.

* **n_threshold**: The the number of verbatim comments which must appear before an appendix of
coded comments will be included. This defaults to 15, but it can be set to any level. Split appendices may require 
a lower n_threshold since some subgroups are smaller.

* **code_type**: The type of coded comment data export. These two  types of data exports are described above.
If no code_type is specified, the default is to use NVivo crosstab export with the ResponseID in the first row and
second column labeled with the varnmae and containing response presence
1/0 indicator. For old filemaker pro format, use "fmp" specification.

* **filename**: The desired name of the output file including extension (e.g. .docx). If this is not specified, 
it will default to "Text Appendices with Coded Comments.docx".

  * `filename` is relevant for make_coded_comments ONLY. Split coded comment appendices generated using 
  make_split_coded_comments on the command line will be named based on the split group.
  
* **split_by**: A list specifying which columns of the response date should be used to split the respondents. This
can be one column or a combination of columns. The split_by specifications will be used to create filenames 
for split coded comment appendices.

  * `split_by` ia relevant for make_split_coded_comments ONLY, since make_coded_comments is used for overall reports.
  * Example for splitting reports by undergraduate school: `split_by = c("ENorLA")`

### Using the QualtricsTools Shiny App to Create Coded Comment Appendices

This functionality is under development as of spring 2020 but is not yet available. Please use the command 
line to generate coded comment appendices.
