---
title: Creating Text Appendices with Coded Comments
---

QualtricsTools makes it easy to create survey summary report appendices of full text comments using 
`make_text_appendices` and `make_split_text_appendices`. In addition, users can easily make 
text appendices that include both full text comments and frequency reports of categorized "coded comments"
using the functions `make_coded_comments` and `make_split_coded_comments`.

Coded comments must follow one of two standardized formats (see below for details and examples).
These coded comment data formats correspond to how Tufts Office of Institutional Research 
codes and exports coded comment data. The parameter `code_type` specifies whether
the coded comment data are exported from FileMaker Pro (or have been modified to appear as such)
or exported from NVivo using the matrix export.


## Coded Comment Appendices with the Command Line in R

There are two functions to create coded comment appendices:

1. **make_coded_comments** creates coded comment appendix for an overall survey summary report
2. **make_split_coded_comments** creates coded comment appendices for split supgroup reports

Both of these functions require the following arguments (input):

* **qsf_path**: The path location of the .qsf file to be processed. This must be passed as text string (surrounded by "") 
and, on a Windows machine, all '\' must be replaced by '/'. If no qsf_path is provided, the user will be asked to choose 
a qsf.

* **csv_path**: The string path location of the .csv file to be processed. This requires path specifications as above. 
If no csv_path is provided, the user will be prompted to choose from the dialogue box.

* **headerrows**: Specifies the number of header rows in the CSV data. 
Use 3 for data exported under current OIR specifications (legacy exporter, unchecked legacy view results)

* **sheets_dir**: The string path location of the directory which contains Excel documents for each coded comment 
using one of the two formats specified. All coded comments must use the same data output format that follows the 
NVivo or FileMaker Pro export format.

* **output_dir**: The string path for the directory to which R should write the coded comment report. If not specified,
your coded comment appendix will be written to a temporaryy file.

* **n_threshold**: The the number of verbatim comments which must appear before an appendix of
coded comments will be included. This defaults to 15, but it can be set to any level. Split appendices may require 
a lower n_threshold since some subgroups are smaller.

* **code_type**: The type of coded comment data export. These two  types of data exports are described above.
If no code_type is specified, the default is to use NVivo crosstab export with the ResponseID in the first row and
second column labeled with the varnmae and containing response presence
1/0 indicator. For old filemaker pro format, use "fmp" specification.

* **filename**: The desired name of the output file including extension (e.g. .docx). If this is not specified, 
it will default to "Text Appendices with Coded Comments.docx".

  * `filename` is relevant for make_coded_comments ONLY. Split coded comment appendices generated using 
  make_split_coded_comments on the command line will be named based on the split group.
  
* **split_by**: A list specifying which columns of the response date should be used to split the respondents. This
can be one column or a combination of columns. The split_by specifications will be used to create filenames 
for split coded comment appendices.

  * `split_by` ia relevant for make_split_coded_comments ONLY, since make_coded_comments is used for overall reports.
  * Example for splitting reports by undergraduate school: `split_by = c("ENorLA")`

## Coded Comment Appendices with the QualtricsTools App

This functionality is under development as of Spring 2020 but is not yet available. Please use the command 
line to generate coded comment appendices.


## Formatting Coded Comment Data for QualtricsTools

Examples of coded comment data exports for each `code_type` format are included in the QualtricsTools package.
In the prescribed workflow, each individual text entry component of a survey 
which needs to be categorized must have a corresponding coded comments ,xlsx file
in the specified `sheets_dir`. The example below has only one question with coded comments,
but the coded comment appendix functions will add coded comment tables for any text entry 
survey question or question component which has a corresponding excel sheet. 


### NVivo Matrix Export

NVivo is useful for coding comments and the tool that Tufts OIR uses as of April 2020. 
When coding comments with NVivo, use the matrix export for each node to produce a coded comment table
compatible with QualtricsTools (`code type = nvivo`). Coded comments using the `code_type` specification 
"nvivo" contain an unlabeled first column of **ResponseIDs**. 
The second column is labeled with the **variable name** and includes 1's and 0's indicating
response presence for each respondent (i.e. did the person respond to the question). 
The variable name in the second column header will be used to link
coded comment responses to the appropriate survey question. 
NVivo matrix export can include data for all respondents, The response presence column will be used 
to filter out non-respondents and provide an accurate count of total comments coded.
Columns to the right of the named response presence column contain coded category data. 
Each column has a coded comment category as its headers with 1's and 0's indicating whether 
the row's response was assigned to that category. Matrix exports from NVivo
may also contain a "Total" column. This "Total" column is not necessary and will be ignored
when creating the coded comment table.

Sample data are shown below to illustrate the `code_type = "nvivo"` data export format.

```{r nvivo-data-export-sample, echo=FALSE, message = FALSE}
library(QualtricsTools)
nvivo_data_path <- here::here("data/Sample Surveys/Better Sample Survey/Comment Coding NVivo/Q5 Coded_NVivo.xlsx")
coded_comment_nvivo <- readxl::read_excel(nvivo_data_path,.name_repair = "minimal")
options(knitr.kable.NA = '')
knitr::kable(coded_comment_nvivo, format='markdown')

```


### FileMaker Pro Export
Prior to adopting NVivo for comments coding, Tufts OIR used FileMaker Pro (FMP) to code comments. Coded Comment data
exported form FileMaker can be turned into coded comment appendices with the code_type specification "fmp".
FMP data exports must contain **ResponseID** in the first column. There must be a column named **varname** 
that includes the variable name values in all rows. Any columns between the initial **ResponseID** and **varname** 
The column immediately right of **varname** is labeled with the question text and contains full 
response text for each respondent. Columns to the right of this included coded comment data. 
Each column title represents a coded comment category, and "1" entries in cells indicate that a respondent's
response has been assigned to that category. 

Sample data are shown below to illustrate the `code_type = "fmp"` data export format.

```{r fmp-data-export-sample, echo=FALSE, message = FALSE}
library(QualtricsTools)
fmp_data_path <- here::here("data/Sample Surveys/Comment Coding/Coded Comments/Q5 Coded.xlsx")
coded_comment_fmp <- readxl::read_excel(fmp_data_path)
options(knitr.kable.NA = '')
knitr::kable(coded_comment_fmp, format='markdown')

```


### A Note on Coded Comment Data Export Types

Tufts OIR transitioned their comment coding process from FMP to NVivo in Summer 2018. 
Between Summer 2018 and Spring 20202, data exported from NVivo was manually modified to 
mimic FMP data export format so the data would be compatible for QualtricsTools. 
As of April 2020, QualtricsTools functions to create coded comment appendices have been 
modified to accept the `code_type` parameter specification and will work with data exported 
under either format. Please look at the coded comment data files when generating 
reports from older surveys that may have coded comments prepared in FMP or using the NVivo to FMP manual 
manipulations. Use `code_type="fmp"` specification to generate appendices from these data.

## Sample Output from make_coded_comments

Below is a sample of the coded comment appendix file created using make_coded comments.
In this example, I have specified `n_threshold = 5` since there are only six responses
to the text question q5_position.


```{r load_coded_comment_data, echo=FALSE}
library(shiny)
library(QualtricsTools)

# Grab the sample survey data from our repository.
qsf <- RCurl::getURL("https://raw.githubusercontent.com/emma-morgan/QualtricsTools/master/data/Sample%20Surveys/Better%20Sample%20Survey/Better_Sample_Survey.qsf")
csv <- RCurl::getURL("https://raw.githubusercontent.com/emma-morgan/QualtricsTools/master/data/Sample%20Surveys/Better%20Sample%20Survey/Better_Sample_Survey.csv")

# Write the sample survey data to file.
qsf_tempfile_path = tempfile()
csv_tempfile_path = tempfile()
write(x = qsf, file = qsf_tempfile_path)
write(x = csv, file = csv_tempfile_path)

# Download the sample coded comments
url <- "https://github.com/emma-morgan/QualtricsTools/blob/master/data/Sample%20Surveys/Comment%20Coding/Coded%20Comments/Q5%20Coded.xlsx?raw=true"
coded_comments_directory <- file.path(tempdir(), basename(tempfile(pattern="")))
dir.create(path = coded_comments_directory)
filename <- "Q5 Coded.xlsx"
coded_comments_filepath <- file.path(coded_comments_directory, filename)
download.file(url, coded_comments_filepath, mode="wb")
```

```{r echo=FALSE, message=FALSE}
output_filepath <- make_coded_comments(
  qsf_path = qsf_tempfile_path,
  csv_path = csv_tempfile_path,
  headerrows = 3, 
  sheets_dir = coded_comments_directory,
  n_threshold = 0,
  filename = "ExampleHTMLCodedComments.html",
  code_type = "fmp"
)
```

```{r render-html}
# We use the includeHTML function from the shiny package to 
# render the HTML output.
includeHTML(output_filepath)
```


The `n_threshold` parameter which is passed above as 0 is the threshold for which coded comments frequency tables with a total number of responses less than `n_threshold` are not included. The parameter defaults to 15 if it is not specified. For example, when we render the report with the `n_threshold = 15` default parameter we see that the coded comments frequency table is not included in the report:

```{r coded-comment-sample-report}
output_filepath <- make_coded_comments(
  qsf_path = qsf_tempfile_path,
  csv_path = csv_tempfile_path,
  headerrows = 3, 
  sheets_dir = coded_comments_directory,
  filename = "ExampleHTMLCodedComments.html",
  code_type = "fmp"
)

shiny::includeHTML(output_filepath)
```
